Non-word repetition in Yélî Dnye

### 2020-12-21 manuscript.Rmd
add conclusions draft

author: 
  - name          : "Alejandrina Cristia"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "29, rue d’Ulm, 75005 Paris, France"
    email         : "alecristia@gmail.com"
  - name          : "Marisa Casillas"
    affiliation   : "2"
    address       : "Wundtlaan 1, 6525 XD, Nijmegen, The Netherlands"
    email         : "marisa.casillas@mpi.nl"

affiliation:
  - id            : "1"
    institution   : "Laboratoire de Sciences Cognitives et de Psycholinguistique, Département d'Etudes cognitives, ENS, EHESS, CNRS, PSL University"
  - id            : "2"
    institution   : "Max Planck Institute for Psycholinguistics"

@@

>>>>

author: 
  - name          : "Alejandrina Cristia"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "29, rue d’Ulm, 75005 Paris, France"
    email         : "alecristia@gmail.com"
  - name          : "Marisa Casillas"
    affiliation   : "2,3"
    address       : "Wundtlaan 1, 6525 XD, Nijmegen, The Netherlands"
    email         : "marisa.casillas@mpi.nl"

affiliation:
  - id            : "1"
    institution   : "Laboratoire de Sciences Cognitives et de Psycholinguistique, Département d'Etudes cognitives, ENS, EHESS, CNRS, PSL University"
  - id            : "2"
    institution   : "Max Planck Institute for Psycholinguistics"
  - id            : "3"
    institution   : "University of Chicago"

@@

### Conclusions

While NWR can, in theory, be used to test a variety of questions about phonological development in any language, previous work has been primarily limited to a handful of related languages spoken in urban, industrialized contexts. The present study shows that, not only can NWR be adapted for very different populations than have previously been tested, but that effects of age and typological frequency may strongly influence phonological development across these diverse settings, while effects of item length, participant gender, maternal education, and birth order, may either have little impact on this facet of language development or have an impact that vaies depending on the linguistic, cultural, and sociodemographic properties of the population under study. Because these latter predictors strongly relate to other language outcomes, the present findings raise the issue of why NWR would pattern differently, what that could tell us about the relationship between lexical development, phonological development, and the input environment and, last but not least, what is implied about the joint applicability of these outcome measures as a diagnostic indicator for language delays and disorders. In the meanwhile, we take the present findings as robustly supporting the idea that phonological development continues well past early childhood and as yielding preliminary support for a connection between individual learners and global language patterns when it comes to acoustic and articulatory markedness.

### 2020-12-21 manuscript.tex
add conclusions draft

\title{Non-word repetition in Yélî Dnye}
\author{Alejandrina Cristia\textsuperscript{1}~\& Marisa
Casillas\textsuperscript{2}}
\date{}

@@

>>>>

\title{Non-word repetition in Yélî Dnye}
\author{Alejandrina Cristia\textsuperscript{1}~\& Marisa
Casillas\textsuperscript{2,3}}
\date{}

@@

\subsubsection{Conclusions}\label{conclusions}

While NWR can, in theory, be used to test a variety of questions about
phonological development in any language, previous work has been
primarily limited to a handful of related languages spoken in urban,
industrialized contexts. The present study shows that, not only can NWR
be adapted for very different populations than have previously been
tested, but that effects of age and typological frequency may strongly
influence phonological development across these diverse settings, while
effects of item length, participant gender, maternal education, and
birth order, may either have little impact on this facet of language
development or have an impact that vaies depending on the linguistic,
cultural, and sociodemographic properties of the population under study.
Because these latter predictors strongly relate to other language
outcomes, the present findings raise the issue of why NWR would pattern
differently, what that could tell us about the relationship between
lexical development, phonological development, and the input environment
and, last but not least, what is implied about the joint applicability
of these outcome measures as a diagnostic indicator for language delays
and disorders. In the meanwhile, we take the present findings as
robustly supporting the idea that phonological development continues
well past early childhood and as yielding preliminary support for a
connection between individual learners and global language patterns when
it comes to acoustic and articulatory markedness.
